---
title: "Rebrickable analysis"
author: "Mateusz Czajka"
date: "2023-12-05"
output:
  html_document: 
    toc: yes
    toc_float: yes
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)
```
# Libraries
```{r, echo=TRUE}
library(ggplot2)
library(dplyr)
library(skimr)
library(png)
library(grid)
library(plotly)
```
# Load data
```{r, cache=TRUE, echo=TRUE}
load_csv <- function(csv_name, data_folder = 'data') {
  df <- read.csv(file.path(data_folder, csv_name))
  as_tibble(df)
}

inventories_df <- load_csv('inventories.csv')
inventory_sets_df <- load_csv('inventory_sets.csv')
sets_df <- load_csv('sets.csv')
themes_df <- load_csv('themes.csv')
inventory_minifigs_df <- load_csv('inventory_minifigs.csv')
minifigs_df <- load_csv('minifigs.csv')
inventory_parts_df <- load_csv('inventory_parts.csv')
colors_df <- load_csv('colors.csv')
parts_df <- load_csv('parts.csv')
elements_df <- load_csv('elements.csv')
part_categories_df <- load_csv('part_categories.csv')
part_relationships_df <- load_csv('part_relationships.csv')
```

```{r}
dataframes_list <- list(
  inventories = inventories_df,
  inventory_sets = inventory_sets_df,
  sets = sets_df,
  themes = themes_df,
  inventory_minifigs = inventory_minifigs_df,
  minifigs = minifigs_df,
  inventory_parts = inventory_parts_df,
  colors = colors_df,
  parts = parts_df,
  elements = elements_df,
  part_categories = part_categories_df,
  part_relationships = part_relationships_df
)

dataframes_names <- names(dataframes_list)
```

# Basic tables analysis
## Data schema
```{r}
image_path <- "data/rebrickable_schema_v3.png"
rebrickable_schema <- readPNG(image_path)

image_plot <- ggplot() +
  annotation_custom(
    rasterGrob(
      rebrickable_schema, 
      interpolate = TRUE
    ), 
    xmin = -Inf, 
    xmax = Inf, 
    ymin = -Inf, 
    ymax = Inf) +
  theme_void()

image_plot
```

## Tables
```{r, comment=NA}
printBasicSummary <- function(df) {
  knitr::kable((head(df)))
  skim(df)
}
```

### Inventories
```{r}
  knitr::kable((head(inventories_df)))
  skim(inventories_df)
```
### Inventory sets
```{r}
  knitr::kable((head(inventory_sets_df)))
  skim(inventory_sets_df)
```
### Sets
```{r}
  knitr::kable((head(sets_df)))
  skim(sets_df)
```
### Themes
```{r}
  knitr::kable((head(themes_df)))
  skim(themes_df)
```
### Inventory Minifigs
```{r}
  knitr::kable((head(inventory_minifigs_df)))
  skim(inventory_minifigs_df)
```
### Minifigs
```{r}
  knitr::kable((head(minifigs_df)))
  skim(minifigs_df)
```
### Inventory parts
```{r}
  knitr::kable((head(inventory_parts_df)))
  skim(inventory_parts_df)
```
### Colors
```{r}
  knitr::kable((head(colors_df)))
  skim(colors_df)
```
### Parts
```{r}
  knitr::kable((head(parts_df)))
  skim(parts_df)
```
### Elements
```{r}
  knitr::kable((head(elements_df)))
  skim(elements_df)
```
### Part Relationships
```{r}
  knitr::kable((head(part_relationships_df)))
  skim(part_relationships_df)
```
### Part categories
```{r}
  knitr::kable((head(part_categories_df)))
  skim(part_categories_df)
```
## Dataframes size
```{r, comment=NA}
  count_all_rows <- 0
  count_all_columns <- 0
  count_all_values <- 0
  
  for (df in dataframes_list) {
    dimensions <- dim(df)
      
    count_all_rows <- count_all_rows + dimensions[1]
    count_all_columns <- count_all_columns + dimensions[2]
    count_all_values <- count_all_values + dimensions[1] * dimensions[2]
  }
  
  cat("All rows in dataframes: ", as.character(count_all_rows), "\n")
  cat("All columns in dataframes: ", as.character(count_all_columns), "\n")
  cat("All values in dataframes: ", as.character(count_all_values), "\n")
```

# Analysis deep dive
### Themes
#### Themes sum of rows with NA value
```{r}
sum(is.na(themes_df))
```
All NA values are in parent_id column
```{r}
themes_df %>% summarise(across(everything(), ~ sum(is.na(.))))
```

Create themes_parent_df
```{r}
themes_parent_df <- subset(themes_df, is.na(parent_id))
themes_parent_df <- themes_parent_df %>% select(-parent_id)
themes_parent_df
```
Join themes_parent_df with themes_df, insert name_child into name_parent if name_parent is NA
```{r}
themes_with_parents_df <- left_join(themes_df, themes_parent_df, by = join_by(parent_id == id), suffix = c("_child", "_parent"))
themes_with_parents_df <- themes_with_parents_df %>%
  select(-parent_id) %>%
  mutate(name_parent = ifelse(is.na(name_parent), name_child, name_parent)) %>%
  print()
```
### Sets
#### Sets sum of rows with NA value
```{r}
sum(is.na(sets_df))
```

#### Correlation between year and num_parts
```{r}
year_num_parts_df <- select(sets_df, year, num_parts)

ggplot(year_num_parts_df, aes(x = year, y = num_parts)) +
  geom_point(color="#225555") +
  labs(title = "Scatter Plot of Year vs. Number of Parts",
       x = "Year",
       y = "Number of Parts")
```
```{r}
grouped_by_year <- sets_df %>%
  group_by(year) %>%
  summarise(
    count_sets = n(),
    sum_parts = sum(num_parts),
    mean_parts = mean(num_parts),
    median_parts = median(num_parts),
    min_parts = min(num_parts),
    max_parts = max(num_parts)
  )

ggplot(grouped_by_year, aes(x = year, y = count_sets)) +
  geom_line(stat = "identity") +
  geom_smooth(color="#222255") +
  labs(title = "Sum of sets in each year",
       x = "Year",
       y = "Sum of sets") +
  theme_bw()
```
```{r}
ggplot(grouped_by_year, aes(x = year, y = sum_parts)) +
  geom_line(stat = "identity") +
  geom_smooth(color="#222255") +
  labs(title = "Sum of parts in each year",
       x = "Year",
       y = "Sum of parts") +
  scale_y_continuous(labels = scales::number_format()) +
  theme_bw()
```

#### Join sets with prepared themes
```{r}
sets_themes <- left_join(sets_df, themes_with_parents_df, by = join_by(theme_id == id))
sets_themes <- sets_themes %>% select(-set_num, -theme_id, -img_url, -name)
sets_themes
```
156 Parent themes with number of sets and sum of parts
```{r}
themes_data <- sets_themes %>%
  group_by(name_parent) %>%
  summarize(
    count_sets = n(),
    sum_parts = sum(num_parts)
  )

themes_data
```

```{r}
plot_ly(
    themes_data, 
    x = ~count_sets, 
    y = ~sum_parts, 
    text = ~name_parent, 
    type = "scatter", 
    mode = "markers",
    marker = list(color="#225555")
  ) %>%
  layout(title = "Sum of parts and sets for each theme",
         xaxis = list(title = "Count Sets"),
         yaxis = list(title = "Sum of Parts"))
```
Top 10 themes based on number of sets
```{r}
top_10_themes <- themes_data %>%
  top_n(10, wt = count_sets) %>%
  arrange(desc(count_sets))

top_10_themes
```

```{r}
ggplot(top_10_themes, aes(x=reorder(name_parent, count_sets), y=count_sets)) +
  geom_bar(stat="identity", fill = "#225555") +
  coord_flip() +
  labs(title = "Number of sets in top 10 most popular themes ",
       x = "Theme name",
       y = "Sum of sets") +
  theme_bw()
```
```{r}
sets_themes_grouped <- sets_themes %>%
  group_by(year, name_parent) %>%
  summarise(
    count_sets = n(),
    sum_parts = sum(num_parts)
  , .groups = 'drop')
```

```{r}
plot_ly(
    sets_themes_grouped, 
    x = ~year, 
    y = ~count_sets, 
    color = ~factor(name_parent),
    type = "scatter",
    mode = "markers",
    text = ~paste("Theme: ", name_parent, "<br>Year: ", year, "<br>Count of Sets: ", count_sets),
    hoverinfo = "text",
    marker = list(size = 7)
  ) %>%
  layout(
    title = "Count of Sets Over Time for Different Themes",
    xaxis = list(title = "Year"),
    yaxis = list(title = "Count of Sets")
  )

```

```{r}
#plot_ly(
#    sets_themes_grouped, 
#    x = ~year, 
#    z = ~sum_parts,
#    y = ~count_sets, 
#    color = ~factor(name_parent),
#    line=list(width=4),
#    text = ~paste("Theme: ", name_parent, "<br>Year: ", year, "<br>Count of Sets: ", count_sets, "<br>Sum of Parts: ", sum_parts),
#    hoverinfo = "text"
#  ) %>%
#  add_lines() %>%
#  layout(
#    title = "Count of Sets and Sum of Parts Over Time for Different Themes",
#    xaxis = list(title = "Year"),
#    zaxis = list(title = "Sum of Parts"),
#    yaxis = list(title = "Count of Sets")
#  )
```



# More analysis (interactive + animations)

# Trends

# Forecasting

